\bf Title

### 2024-01-29 article/paper_padic_spec.tex
Ajout preuve caracterisation, modifs programmation lineaire et preuve couronne

The most interesting aspect in the SNF regarding the resolution of \ref{LP} is that the transition matrices are invertible in $\OK$. Indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such that $z \geq 0$ then $Mz \geq 0$. The latter property is a direct consequence of $\OK$ being a ring and the converse is true if the matrix $M$ is invertible in $\OK$ \corentin{est-ce qu'il y a besoin de le prouver ?}. Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$ $Mz \geq 0$ if and only if $Sz \geq 0$.

That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}. This problem is the optimization problem: \simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
\begin{equation}
  \tag{dLP}\label{dLP}
\begin{array}{rcll}
  p^* & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
  &    & \text{s.t.}         & S y + b' \geq 0
\end{array}
\end{equation}
with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = s_1 \oplus s_2 \oplus \ldots \oplus s_r \oplus { \bm 0}_{m-r} $ for $r={\rm rank} S$.

The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{dLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m(\OK)$ and $ Q \in GL_n(\OK)$ are such that $A = Q^{-1} S P$.

A vector $x^* \in K^n$ is \emph{feasible solution} of \ref{LP} if $Ax^* + b \geq 0$. Similarly, a vector $y^* \in K^n$ is a feasible of \ref{dLP} if $Sy^*+b' \geq 0$. We will denote as $Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{dLP}.

\begin{proposition}\label{prop:reduc}

	We have then the following results
	\begin{enumerate}
		\item $x^*$ is a feasible solution of \ref{LP} if and only if $y^* = P x^*$ is a feasible solution of the associated \ref{dLP} problem.
		\item $x$ is a solution of \ref{LP} if and only if $y = P x$ is a solution of the associated \ref{dLP} and the the infimum is the same.
		\item \ref{dLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, with $r$ the rank of $S$.
		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{dLP} admits feasible solutions it is unbounded and does not have a solution.

@@

\begin{proof}

  First of all, 1. is a consequence of the fact that $Mx^*+b = MP^{-1}y^* +b\geq 0$ if and only if $Q(MP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.

  Then, 2. comes from the fact that for all $c \in K^n$ $\langle c, x\rangle = \langle c, P^{-1}Py \rangle = \langle \left(P^{-1}\right)^T c, y \rangle$.

  A vector $y =  \left[\begin{smallmatrix} y_1 \\ \vdots \\ y_n \end{smallmatrix}\right] \in K^n$ is feasible solution of \ref{dLP} if and only if $\val(s_i y_i + b_i) >=0$ for all $i \in \{1...n\}$ \corentin{préciser les notations}. 
  However, $s_i =0$ for $n-r \leq i\leq n$. Therefore, \ref{dLP} have solution only if the $m-r$ last coefficient of b' are zero.

@@

  Finally, let $y^*$ be a feasible solution of \ref{dLP}. Let us suppose there exists $r+1 \leq i \leq m$ such that $c'_i \neq  0$ and fix such $i$. Let us then consider the vector $e^i$ whose only non-zero coefficient is the $i-$th, which is $1$. Then $y^*+\lambda e^i$ is a feasible solution for all $\lambda \in K$ and $\langle c', y^* + \lambda e^i\rangle = \langle c' , y^* \rangle + \lambda c'_i$. In particular, for $\lambda = -\frac{\langle c', y^* \rangle}{c'_i}$ $\val \left( \langle c', y^* + \lambda e ^i \rangle\right) = \val (0) = + \infty$.

\end{proof}

The two first points of the proposition \ref{prop:reduc} show that we can resolving a linear program is equivalent to resolution the associated \ref{dLP} problem. Furthermore, if one considers only the iteration of \ref{dLP} which have solutions. By point 3. and 4. of proposition \ref{prop:reduc} one can reduce the problem by only taking acount only the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and which coefficients are exactly the nonzero invariants factors. The set $Adm$ of the feasible solutions can then be written as the set of vectors $y \in \mathbb{Q}_{ p } ^n$ that verifies $\forall 1 \le i\le r \ s_i y_i + b'_i \in \OK$ i.e. that verifies :

\begin{equation}
	\forall 1 \le i\le r  \ y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK
\end{equation}

Resolving \ref{dLP} consists in minimizing $\val\left(\left<c',y \right>\right)$ over $Adm$. The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be rewritten in $\left<c',Adm \right> = \lambda + \pi^{v} \OK$ with $\lambda = \sum_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.

Finally, two cases can occur depending on $v$ and the valuation of $\lambda$.
\begin{itemize}
	\item If $\val( \lambda) < v$ the minimum of $y\mapsto \val\left(\left<c',y \right>\right)$ over $Adm$ is reached in any point of $Adm$ and is equal to $\val\left( \lambda\right)$.
	\item If $\val\left( \lambda \right) \ge v$ then $\lambda \in \pi^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies 
	\[\val \underset{ \begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}}{\sum} y_{i} = 0. \]

\end{itemize}
\begin{remark}
	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be aplied. The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded and as such does not have any solution. 
\end{remark}

@@

\begin{theorem}
  \label{caracsdp}
  $M \in \allmat_{d,d}^+(K)$ if and only if $\chi_M \in \OK[T]$.
\end{theorem}
\begin{proof}
  \simone{preuve ?}
\end{proof}

@@

\begin{example}
  The reverse inclusion of \Cref{cor_caracsdp} is false in general. For instance the characteristic polynomial of
  $M = (\begin{smallmatrix} 5 + {3}/{5} & {4}/{5} \\ {4}/{5} & -{3}/{5} \end{smallmatrix})$ is $\chi_M = T^2-5T-4$. However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in \allmat_{2,2}^+(\mathbb{Q}_5)$, nevertheless $M \not\in \allmat_{2,2}(\mathbb{Z}_5)$, hence $\allmat_{2,2}^+(\mathbb{Q}_5) \not\subset \allmat_{2,2}(\mathbb{Z}_5)$.
\end{example}

\begin{proposition}
  The set $\allmat_{d,d}^+(K)$ is both open and closed.
\end{proposition}
\begin{proof}
Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{p}[X]$ (\simone{attention p-adique}) equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$ \simone{attention p-adique}. $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ which defines a discrete distance for which open balls are also closed.
Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous. \simone{mmm je dirais plutôt ``the function that maps a matrix to its characteristic polynomial'', n'est-ce pas ?}
\end{proof}

@@

@@

@@

\begin{proof}
Let $A$ be the annuli defined by $a<b \in R^*_+$.

We consider for all $x,y \in K $ the matrix  $$M(x,y) :=
\begin{pmatrix} 
	p^ax & 0 & 0 & 0 \\
	0 & p^{-b}y & 0 & 0 \\
	0 & 0 & p^{-1} & p^{-1}x \\
	0 & 0 & p^{-1}y & - p^{-1}  \\
\end{pmatrix} $$ and the associated spectrahedron $\mathcal{S}= \{(x,y) \in K  : M(x,y) \succeq 0\} $

Let us show that $x \in C$ if and only if  $\exists y \in K(x,y) \in \mathcal{S}$.

Let $x,y$ be two $p$-adic numbers.
$M(x,y)$ can be decomposed in three blocks : $p^ax$, $p^{-b}y $ and $M'(x,y) = \begin{pmatrix} p^{-1} & p^{-1}x \\ p^{-1} y & p^{-1}\end{pmatrix} $. Using \ref{caracsdp} we know that $M(x,y)$ is positive semidefinfite if and only if
$
\begin{cases}
  p^ax \ge 0 \\
  p^{-b}y \ge 0\\
  \text{Tr}M'\left( x,y \right) = 0 \ge 0\\
  \text{det} M'(x,y ) = p^{-2}\left( xy-1 \right)  \ge 0 
\end{cases}
$ 
that is if and only if 
\begin{equation}
	\label{eq:caracsdp} 
	\begin{cases} 
		\val\left(x\right)\ge a\\
		\val\left(y\right)\ge -b\\
		p^{-2} \left( xy-1 \right) \ge 0
	\end{cases}
\end{equation}

Therefore $x \in C$ if and only if there exists $y \in K $ so that $(x, y)$ verifies \ref{eq:caracsdp}. Si $x, y$ verifies indeed \ref{caracsdp} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $p^{-2} \left( xy-1 \right) \ge 0$ implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in $. Reciprocally if $x \in C$ then $(x,x^{-1}) $ verifies \ref{eq:caracsdp}  .
\end{proof}

>>>>

The most interesting aspect in the SNF regarding the resolution of \ref{LP} is that the transition matrices are invertible in $\OK$. Indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such that $z \geq 0$ then $Mz \geq 0$. The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$. Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$ $Mz \geq 0$ if and only if $Sz \geq 0$.

That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}. This problem is the optimization problem: \simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
\begin{equation}
  \tag{DLP}\label{DLP}
\begin{array}{rcll}
  p^* & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
  &    & \text{s.t.}         & S y + b' \geq 0
\end{array}
\end{equation}
with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = s_1 \oplus s_2 \oplus \ldots \oplus s_r \oplus { \bm 0}_{m-r} $ for $r={\rm rank} S$.

%The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{DLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m(\OK)$ and $ Q \in GL_n(\OK)$ are such that $A = Q^{-1} S P$.

A vector $x^* \in K^n$ is \emph{feasible solution} of \ref{LP} if $Ax^* + b \geq 0$. Similarly, a vector $y^* \in K^n$ is a feasible of \ref{DLP} if $Sy^*+b' \geq 0$. We will denote as $Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{DLP}.

\begin{proposition} 
  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S \in \allmat_{m,n}(K)$ be the Smith normal form of $A$ with transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL(\OK)$ such that $A=Q^{-1}SP$.
  We define $b':= Qb$ and $c':= (P^{-1})^Tc$. 
   \begin{enumerate}
    \item $x^* \in K^n$ is a feasible solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y^* = P x^*$ is a feasible solution of the \ref{DLP} problem of parameters $S, b'$ ans $c'$.
		\item $x \in K^n$ is a solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y = P x$ is a solution of the \ref{DLP} problem of parameters $S,b'$ and $c'$ and $\langle c,x \rangle = \langle c',y \rangle$.
   \end{enumerate}
\end{proposition}
\begin{proof}
  First of all, 1. is a direct consequence of the fact that $Ax^*+b = AP^{-1}y^* +b\geq 0$ if and only if $Q(AP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.

  Then, 2. comes from the fact that for all $c \in K^n$ $\langle c, x\rangle = \langle c, P^{-1}Py \rangle = \langle \left(P^{-1}\right)^T c, y \rangle$.
\end{proof}

The last proposition allows to only consider the resolution of the \ref{DLP} problem.
\begin{proposition}\label{prop:reduc}

	We have then the following results
	\begin{enumerate}

		\item \ref{DLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, with $r$ the rank of $S$.
		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{DLP} admits feasible solutions it is unbounded and does not have a solution.

@@

\begin{proof}
  A vector $y =  \left[\begin{smallmatrix} y_1 \\ \vdots \\ y_n \end{smallmatrix}\right] \in K^n$ is feasible solution of \ref{DLP} if and only if $\val(s_i y_i + b_i) >=0$ for all $i = 1...n$ \corentin{préciser les notations}. 
  However, $s_i =0$ for $n-r \leq i\leq n$. Therefore, \ref{DLP} have solution only if the $m-r$ last coefficient of b' have nonnegative valuation.

@@

  Finally, let $y^*$ be a feasible solution of \ref{DLP}. Let us suppose there exists $r+1 \leq i \leq m$ such that $c'_i \neq  0$ and fix such $i$. Let us then consider the vector $e^i$ whose only non-zero coefficient is the $i-$th, which is $1$. Then $y^*+\alpha e^i$ is a feasible solution for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$. In particular, for $\alpha = -\frac{\langle c', y^* \rangle}{c'_i}$, $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val (0) = + \infty$. 
\end{proof}

From now on, we will only consider the iterations of \ref{DLP} which have solutions, by \ref{prop:reduc}, we can then reduce the problem by only taking acount only the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and whose coefficients are exactly the nonzero invariants factors. 
The set $Adm$ of the feasible solutions can then be written as the set of vectors $y \in K^n$ that verifies $ \ s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.} $Adm = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :\ y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}$.

Resolving \ref{DLP} consists (by definition) in minimizing $y \mapsto \val\left(\left<c',y \right>\right)$ over $Adm$. The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be expressed as $\left<c',Adm \right> = \lambda + \pi^{v} \OK$ with $\lambda = \sum_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
Finally, two cases can occur depending on $v$ and the valuation of $\lambda$. If $\val( \lambda) < v$ the minimum of $y\mapsto \val\left(\left<c',y \right>\right)$ over $Adm$ is reached in any point of $Adm$ and is equal to $\val\left( \lambda\right)$. Whereas, if $\val\left( \lambda \right) \ge v$ then $\lambda \in \pi^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies 
	\[\val \underset{ \begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}}{\sum} y_{i} = 0. \]

\begin{remark}
	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be aplied. The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded and as such does not have any solution. 
\end{remark}

@@

\begin{theorem}
  \label{caracsdp}
  $M \in \allmat_{d,d}^+(K)$ if and only if $\chi_M \in \OK[T]$.
\end{theorem}
\begin{proof}
  Both senses of the equivalence will be proven by contraposition.

  Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
  Firstly, suppose   $M \not \in \allmat_{d,d}^+(K)$ {\it i.e.} $\chi_M$ have a root $\rho$ of negative valuation.
  It follows that $\val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i \right) = + \infty$ and $\val \rho^d = d \val \rho <0$.
  The properties of the non-archimedean inequality followed by $\val $ implie that $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) = \val \rho^d$ and $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) \ge \min \limits_{i=0,..., d-1} \val \left(a_i \rho^i\right)$. Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^d$ {\it i.e.} such that $\val (a_i) \le (d-i) \val \rho <0$. That is all the results we need to prove the result.

  We have proven the converse sense of the equivalence. To prove the direct sense a brief introduction to Newton's polygon will be needed, we will only state the results we use in this proof and will redirect to \cite{gouvea_p-adic_2003} to further explanations.
  The Newton polygon $\mathcal{P}$ of a polynomial $P = \sum_{n}^{i=0} a_i T^i \in K[T]$ is defined as the inferior convex hull of the set $\{(i, \val a_i ) | i\in \{0,...,d\} \}$ {\it i.e.} the largest convex function $\mathcal{P} : [0,n] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$ for $i=1,...,n$. 
  This function is piecewise affine and its slopes are exactly the opposites of the valuations of the roots of $P$. These are all the results we will need for this proof.

  Suppose $\chi_M \not\in \OK[T]$. There exists $j \in \{0,...,d-1\}$ such that $\val (a_j)<0$. The polynomial $\chi_M$ being monic the point with abscissa $n$ of $\chi_M$'s Newton's Polygon is $(n,0)$. 
  Therefore, the point $(j, \val a_j)$ having negative ordinate implies that at least one of the slopes of $\chi_M$'s Newton's Polygon is positive so that $\chi_M$ has a root with negative valuation.
\end{proof}

@@

\begin{example}
  The reverse inclusion of \Cref{cor_caracsdp} is false in general. For instance the characteristic polynomial of
  $M = \left(\begin{smallmatrix} 5 + {3}/{5} & {4}/{5} \\ {4}/{5} & -{3}/{5} \end{smallmatrix}\right)$ is $\chi_M = T^2-5T-4$. However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in \allmat_{2,2}^+(\mathbb{Q}_5)$, nevertheless $M \not\in \allmat_{2,2}(\mathbb{Z}_5)$, hence $\allmat_{2,2}^+(\mathbb{Q}_5) \not\subset \allmat_{2,2}(\mathbb{Z}_5)$.
\end{example}

\begin{proposition}
  The set $\allmat_{d,d}^+(K)$ is both open and closed.
\end{proposition}
\begin{proof}
Firstly, $\OK[X]$ is closed and open in $K[X]$ equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|$. $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for which open balls are also closed sets.
Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
\end{proof}

@@

\begin{definition}
  A \emph{cone} is subset $C$ of $K^d$ that is closed under multiplication by elements of $\OK$.   
\end{definition}

\begin{remark}
  \corentin{Pas nécessairement très important, à voir}
  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
\end{remark}

\begin{proposition}
  The set $\allmat^+_{d,d}(K)$ is a cone.
\end{proposition}
\begin{proof}
  The result is immediate following the definiton of $\allmat^+_{d,d}(K)$.
\end{proof}

@@

\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
\begin{definition}[Alternative definition]
  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$. 
  We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$. 
  The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
\end{definition}

@@

\begin{proof}
Let $A$ be the annuli defined by $a<b \in R^*_+$. We consider for all $x,y \in K $ the spectrahedron $\mathcal{S}= \left\{(x,y) \in K  : M(x,y) := \pi^ax \oplus \pi^{-b}y \oplus \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix} \succeq 0\right\}$.

We will show that $x \in A$ if and only if  there exists $y\in K$ such that $(x,y) \in \mathcal{S}$.

Let $x,y \in K$. By \ref{caracsdp}, $M(x,y)$ is positive semidefinite if and only if $(x,y)$ is a solution of \ref{eq:annulussyst}.

\begin{equation}
  \label[type]{eq:annulussyst}
\begin{cases}
  \val(\pi^ax) \ge 0 \\
  \val(\pi^{-b}y) \ge 0\\
  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
  \val(\pi^{-2}\left( xy-1 \right))  \ge 0 
\end{cases}
\iff	
\begin{cases} 
		\val\left(x\right)\ge a\\
		\val\left(y\right)\ge -b\\
		\val\left( xy-1 \right) \ge 2
	\end{cases}
\end{equation}

Therefore, if $(x, y)$ verifies \ref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$. The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$.

Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \ref{eq:annulussyst} .
\end{proof}
